Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-04-26 Paper/Manuscript.tex
fix a few missing symbols uses

Target strength can then be estimated using Eq. \ref{eq:TS}:
\begin{equation}
\label{eq:TS_f}
\ts(\freqsym) = 10\log_{10}(\prxetf(\samplesymf)) + 40\log_{10}(\range_t) + 2\absorp(\freqsym)\range_t - 10\log_{10}\left( \frac{\ptxe \wlen^2 \gain^2(\along_t,\athw_t,f)}{16\pi^2} \right)
\end{equation}
where the sample index $\samplesymf$ corresponding to frequency $\freqsym$ can be estimated using
\begin{equation}
\label{eq:m(f)}
\samplesymf = \lfloor \frac{\freqsym}{\fsdec} \ndft \rfloor \mod \ndft
\end{equation}
%
\begin{figure}
\includegraphics[width=16cm]{Fig_TS}
\caption{\label{fi:TS}The discrete Fourier transform of the target signal $\ypctargetf(\samplesymf)$ (a) and the reduced auto correlation signal $\ymfautoredf(\samplesymf)$ (b), the normalized discrete Fourier transform of the target signal $\ypctargetnormf(\samplesymf)$ (c), gain (d) and the estimated TS(f) (e).}
\end{figure}

A frequency modulated pulse scattered by a metallic sphere will exhibit frequencies at which very little energy is returned due to destructive interference \citep{stanton2008}. This is visible in the $\ts$ (Fig. \ref{fi:TS}) and agrees well with theoretical estimates of the backscatter from spheres \citep{maclennan1981}. The amplitude of the backscatter signal also clearly shows these nulls (Fig. \ref{fi:TS}), which are readily visible here due to the use of a linear chirp where time through the pulse corresponds to specific frequencies.

@@

\begin{figure}
\includegraphics[width=16cm]{Fig_Sv_echogram}
\caption{\label{Fig_Sv_echogram} Sv as a function of frequency ($samplesymf$) and range ($samplesymt$) for a echogram raw data file. The red vertical line indicates the ping processed in this section.}
\end{figure}

@@

\begin{figure}
\includegraphics[width=16cm]{Fig_Sv_m_n}
\caption{\label{Fig_Sv_m_n} Sv as a function of frequency ($\samplesymf$) and range ($\samplesymt$) for a single ping}
\end{figure}

>>>>

Target strength can then be estimated using Eq. \ref{eq:TS}:
\begin{equation}
\label{eq:TS_f}
\ts(\freqsym) = 10\log_{10}(\prxetf(\samplesymf)) + 40\log_{10}(\range_t) + 2\absorp(\freqsym)\range_t - 10\log_{10}\left( \frac{\ptxe \wlen^2 \gain^2(\along_t,\athw_t,f)}{16\pi^2} \right)
\end{equation}
where the sample index $\samplesymf$ corresponding to frequency $\freqsym$ can be estimated using
\begin{equation}
\label{eq:m(f)}
\samplesymf = \lfloor \frac{\freqsym}{\fsdec} \ndft \rfloor \mod \ndft
\end{equation}
%
\begin{figure}
\includegraphics[width=16cm]{Fig_TS}
\caption{\label{fi:TS}The discrete Fourier transform of the target signal $\ypctargetf(\samplesymf)$ (a) and the reduced auto correlation signal $\ymfautoredf(\samplesymf)$ (b), the normalized discrete Fourier transform of the target signal $\ypctargetnormf(\samplesymf)$ (c), gain (d) and the estimated TS(f) (e).}
\end{figure}
%
A frequency modulated pulse scattered by a metallic sphere will exhibit frequencies at which very little energy is returned due to destructive interference \citep{stanton2008}. This is visible in the $\ts$ (Fig. \ref{fi:TS}) and agrees well with theoretical estimates of the backscatter from spheres \citep{maclennan1981}. The amplitude of the backscatter signal also clearly shows these nulls (Fig. \ref{fi:TS}), which are readily visible here due to the use of a linear chirp where time through the pulse corresponds to specific frequencies.

@@

\begin{figure}
\includegraphics[width=16cm]{Fig_Sv_echogram}
\caption{\label{Fig_Sv_echogram} Sv as a function of frequency ($\samplesymf$) and range ($\samplesymt$) for a echogram raw data file. The red vertical line indicates the ping processed in this section.}
\end{figure}

@@

\begin{figure}
\includegraphics[width=16cm]{Fig_Sv_m_n}
\caption{\label{Fig_Sv_m_n} $\sv$ as a function of frequency ($\samplesymf$) and range ($\samplesymt$) for a single ping.}
\end{figure}
